*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-07 Code/Manuscript_O2.Rmd
minor edits

To estimate the Photosynthetic Usable Radiation (PUR), a proxy of incident photons absorbed by the cells, for each *P. marinus* ecotype, the imposed Photosynthetic Active
Radiation (PAR) was first determined using the reported delivery of sinusoidal diel PAR regimes by the Multicultivators, point validated using a LI-250 quantum sensor (LI-COR Inc.,Lincoln, NE, USA). An emission profile from 400 nm to 700 nm of each coloured LED light of the MCMIX-OD Multicultivator and the white LED light of the MC1000-OD Multicultivator was obtained using a Jaz spectrometer (Ocean Optics, Inc.,Dunedin, FL, USA) equipped with a fiber optic cable, HH2 FiberOpticJmp (Part number A901073, Malvern Panalytical Ltd, Malvern, UK). Each LED spectrum was then normalized to its emission maximum. An *in-vivo* whole cell absorbance spectrum for each *P. marinus* strain under each spectral growth condition was obtained using the Olis 14 UV/VIS Clarity Spectrophotometer (Olis Inc., Bogart, GA, USA) to scan across range of λ = 350 nm to 750 nm at 1 nm intervals. The path length of the internally reflective cavity of the Olis spectrophotometer was corrected to a 1 cm path length using the Javorfi correction method [@javorfiQuantitativeSpectrophotometryUsing2006] on PRO 99 media subtracted whole cell absorbance spectra. The blank-corrected whole cell absorbance spectra were normalized to the absorbance maximum of divinyl chlorophyll *a* (Chl a~2~), determined for each spectra, falling between 400 nm and 460 nm.

An integrated weighting equation \@ref(eq:WeightedPUR) [@morelAvailableUsableStored1978] was used to determine the weighted PUR spectrum P(λ); where A(λ) is the blank subtracted, Chl a~2~ peak normalized whole cell absorbance spectrum for each *P. marinus* ecotype, over 400 nm to 700 nm, A(λ); and E(λ) is the peak normalized emission spectrum of the imposed LED growth light, over 400 nm to 700 nm.

@@

Figure \@ref(fig:DNARepairFig) shows genes encoding DNA repair for *P. marinus* strains. As expected, *P. marinus* MED4 possesses the largest, most complete suite of genes encoding DNA repair enzymes, followed by *P. marinus* MIT9313. Conversely, *P. marinus* SS120 demonstrates the smallest genomic capacity for DNA repair. *Prochlorococcus marinus* MED4 and NATL2A were the only strains to possess a gene encoding deoxyribodipyrimidine photolyase, which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003]. *Prochlorococcus marinus* MED4 was also the only strain to possesses a gene encoding DNA ligase, which uses ATP as a cofactor for DNA repair. The absence of genes encoding deoxyribodipyrimidine photolyase and DNA ligase (ATP) in *P. marinus* MIT9313 and *P. marinus* SS120 explain why these two strains cannot tolerate growth under full [O~2~] and high light, found at the ocean surface. Furthermore, the protective effect of lower [O~2~], allowing these strains to grow at higher light, may relate in part to suppression of DNA damage when generation of Reactive Oxygen Species is suppressed at lower [O~2~]. NATL2A, a clade LLI, has been found near the ocean surface during deep ocean mixing [@malmstromTemporalDynamicsProchlorococcus2010]. Malmstrom *et al*. attributes NATL2A tolerance to short exposures of high light to the presence of the genes encoding photolyase, a gene found in HL clades. The presence of deoxyribodipyrimidine photolyase and absence of DNA ligase (ATP) supports why NATL2A tolerates limited exposure to high light and why NATL2A is unable to fully repair damaged DNA.  *Prochlorococcus* are highly susceptible to hydrogen peroxide (H~2~O~2~) toxicity as they lack genes which scavenge H~2~O~2~ molecules [@morrisFacilitationRobustGrowth2008]. The small cell size of *Prochlorococcus* allow the reactive oxygen species (ROS), H~2~O~2~, to cross the cell membrane [@omarDiffusionalInteractionsMarine2022]; however, accumulation of extracellular H~2~O~2~ remains toxic to *Prochlorococcus* [@morrisFacilitationRobustGrowth2008;  @morrisDependenceCyanobacteriumProchlorococcus2011].

>>>>

To estimate the Photosynthetic Usable Radiation (PUR), a proxy of incident photons absorbed by the cells, for each *P. marinus* ecotype, the imposed Photosynthetic Active
Radiation (PAR) was first determined using the reported delivery of sinusoidal diel PAR regimes by the Multicultivators, point validated using a LI-250 quantum sensor (LI-COR Inc.,Lincoln, NE, USA). An emission profile from 400 nm to 700 nm of each coloured LED light of the MCMIX-OD Multicultivator and the white LED light of the MC1000-OD Multicultivator was obtained using a Jaz spectrometer (Ocean Optics, Inc.,Dunedin, FL, USA) equipped with a fiber optic cable, HH2 FiberOpticJmp (Part number A901073, Malvern Panalytical Ltd, Malvern, UK). Each LED spectrum was then normalized to its emission maximum. An *in-vivo* whole cell absorbance spectrum for each *P. marinus* strain under each spectral growth condition was obtained using the Olis 14 UV/VIS Clarity Spectrophotometer (Olis Inc., Bogart, GA, USA) to scan across range of λ = 350 nm to 750 nm at 1 nm intervals. The path length of the internally reflective cavity of the Olis spectrophotometer was corrected to a 1 cm path length using the Javorfi correction method [@javorfiQuantitativeSpectrophotometryUsing2006] on PRO 99 media subtracted whole cell absorbance spectra. The blank-corrected whole cell absorbance spectra were normalized to the absorbance maximum of divinyl chlorophyll *a* (Chl *a*~2~), determined for each spectra, falling between 400 nm and 460 nm.

An integrated weighting equation \@ref(eq:WeightedPUR) [@morelAvailableUsableStored1978] was used to determine the weighted PUR spectrum P(λ); where A(λ) is the blank subtracted, Chl *a*~2~ peak normalized whole cell absorbance spectrum for each *P. marinus* ecotype, over 400 nm to 700 nm, A(λ); and E(λ) is the peak normalized emission spectrum of the imposed LED growth light, over 400 nm to 700 nm.

@@

Figure \@ref(fig:DNARepairFig) shows genes encoding DNA repair for *P. marinus* strains. As expected, *P. marinus* MED4 possesses the largest, most complete suite of genes encoding DNA repair enzymes, followed by *P. marinus* MIT9313. Conversely, *P. marinus* SS120 demonstrates the smallest genomic capacity for DNA repair. *Prochlorococcus marinus* MED4 and NATL2A were the only strains to possess a gene encoding deoxyribodipyrimidine photolyase, which, in the presence of blue light, is responsible for repairing DNA damaged by UV light [@sancarStructureFunctionDNA2003]. *Prochlorococcus marinus* MED4 was also the only strain to possesses a gene encoding DNA ligase, which uses ATP as a cofactor for DNA repair. The absence of genes encoding deoxyribodipyrimidine photolyase and DNA ligase (ATP) in *P. marinus* MIT9313 and *P. marinus* SS120 explain why these two strains cannot tolerate growth under full [O~2~] and high light, found at the ocean surface. Furthermore, the protective effect of lower [O~2~], allowing these strains to grow at higher light, may relate in part to suppression of DNA damage when generation of Reactive Oxygen Species is suppressed at lower [O~2~]. NATL2A, a clade LLI, has been found near the ocean surface during deep ocean mixing [@malmstromTemporalDynamicsProchlorococcus2010]. Malmstrom *et al*. [@malmstromTemporalDynamicsProchlorococcus2010] attributes NATL2A tolerance to short exposures of high light to the presence of the genes encoding photolyase, a gene found in HL clades. The presence of deoxyribodipyrimidine photolyase and absence of DNA ligase (ATP) supports why NATL2A tolerates limited exposure to high light and why NATL2A is unable to fully repair damaged DNA.  *Prochlorococcus* are highly susceptible to hydrogen peroxide (H~2~O~2~) toxicity as they lack genes which scavenge H~2~O~2~ molecules [@morrisFacilitationRobustGrowth2008]. The small cell size of *Prochlorococcus* allow the reactive oxygen species (ROS), H~2~O~2~, to cross the cell membrane [@omarDiffusionalInteractionsMarine2022]; however, accumulation of extracellular H~2~O~2~ remains toxic to *Prochlorococcus* [@morrisFacilitationRobustGrowth2008;  @morrisDependenceCyanobacteriumProchlorococcus2011].
